onsetsync demo

### 2023-01-01 README.Rmd
minor

```{r synch2isochron,fig.width=7, fig.asp=.75}
fig1 <- plot_by_beat(df = CSS_Song2, 
                     instr = c('Bass','Clave','Guitar','Tres'), 
                     beat = 'SD', 
                     virtual='Isochronous.SD.Time',
                     pcols=2)
print(fig1)
```

@@

```{r fig2,warning=FALSE,fig.width=7, fig.asp=.7}
inst <- c('Clave','Bass','Guitar','Tres')              # Define instruments 
dn <- sync_execute_pairs(CSS_Song2, inst, beat = 'SD') # Calculate ansychr.
fig2 <- plot_by_pair(dn)                               # Plot
print(fig2)  
```

>>>>

```{r synch2isochron,fig.width=7.4, fig.asp=.75}
fig1 <- plot_by_beat(df = CSS_Song2, 
                     instr = c('Bass','Clave','Guitar','Tres'), 
                     beat = 'SD', 
                     virtual='Isochronous.SD.Time',
                     pcols=2)
print(fig1)
```

@@

```{r fig2,warning=FALSE,fig.width=7.4, fig.asp=.7}
inst <- c('Clave','Bass','Guitar','Tres')              # Define instruments 
dn <- sync_execute_pairs(CSS_Song2, inst, beat = 'SD') # Calculate ansychr.
fig2 <- plot_by_pair(dn)                               # Plot
print(fig2)  
```
